---
title: 'troubleshooting with training and choice lables'
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/processed.csv")
d.train <- read.csv("../data/processed_training.csv")
```

# Take a look at trianing items
In these trails, F and J keys aren't switching like they should.

```{r}
length(unique(d.train$ID.true))
table(d.train$Task, d.train$Key_value_F)
# Create proportion column

```


```{r}

agr <- d.train %>% 
  group_by(Task) %>% 
  summarize(MeanReactionTime = mean(ReactionTime), 
          CILow = ci.low(ReactionTime), 
          CIHigh = ci.high(ReactionTime)) %>%
  mutate(YMin = MeanReactionTime - CILow, 
         YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```



Plot as a function of trial order

```{r}

agr <- d.train %>% 
  group_by(Task,TrialNumber) %>% 
  summarize(MeanReactionTime = mean(ReactionTime), 
          CILow = ci.low(ReactionTime), 
          CIHigh = ci.high(ReactionTime)) %>%
  mutate(YMin = MeanReactionTime - CILow, 
         YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=TrialNumber,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```





# Order differences?
This is doing something funky...so figure that out


```{r}
agr <- d %>% 
  group_by(Task,TrialNumber) %>% 
  summarize(MeanReactionTime = mean(ReactionTime), 
          CILow = ci.low(ReactionTime), 
          CIHigh = ci.high(ReactionTime)) %>%
  mutate(YMin = MeanReactionTime - CILow, 
         YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=TrialNumber,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


# Look at the test items where there was/wasn't a switch in the lables
#Find participants in test items where F != abstract/negative and J != concrete/positive

```{r}

test.switch <- d %>% 
  # Since training was always F = negative/abstract, switch is the opposite
  filter((Key_value_F %in% c("positive","concrete"))
           # (PennElementType == "Selector")
         ) 
switch.IDs <- test.switch$ID.true

# how many participants have the switch?
length(unique(test.switch$ID.true))

nrow(test.switch)

# View(test.switch)

```

### How does accuracy and RT change in these cases?
Interestingly, Concrete accuracy is higher than for valance?
```{r}
agr <- test.switch %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


```{r}
agr <- test.switch %>% 
  group_by(Task,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


## Look at the ones where there is no switch


```{r}

test.no.switch <- d %>% 
  filter(Key_value_F %in% c("negative","abstract")
         # (PennElementType == "Selector")
         ) 

nrow(test.no.switch)

no.switch.IDs <- test.no.switch$ID.true


# how many participants have the switch?
length(unique(test.no.switch$ID.true))

# how many participants have the switch?
length(unique(d$ID.true))



```

Wait, it's surprising that in the no switch error cases that accuracy would be lower for concrete and higher for valance?

Things to look at:
- is this due to a coding error? are the values for Accuracy getting reversed or something?

```{r}
agr <- test.no.switch %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```

```{r}
agr <- test.no.switch %>% 
  group_by(Task,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


So it seems regardless of BlockOrder....but this must be a miscoding error

can it really be that NO participant is paying attention to the labels in the Concreteness task, but are in the Valence task??

To check out:
- how are these participants doing in the training trials?



```{r}
agr <- test.no.switch %>% 
  group_by(Task,BlockOrder,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=BlockOrder,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


## In the No Switch trials

```{r}

test.no.switch.conc <- test.no.switch %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0) )

test.no.switch.conc$Response.n = as.numeric(test.no.switch.conc$Response.n)

```


```{r}
agr <- test.no.switch.conc %>% 
  group_by(Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Word)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```

## In the Switch trials

```{r}

test.switch.conc <- test.switch %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0) )

test.switch.conc$Response.n = as.numeric(test.switch.conc$Response.n)

```


```{r}
agr <- test.switch.conc %>% 
  group_by(Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Word)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


# Add a switch column

```{r}
# Add Task column
d$Switch <- ifelse(d$Key_value_F %in% c("concrete","positive"), "Switch","NoSwitch")
d$Response.n = as.numeric(d$Response)

```


What we can see from the following graph, is that the key labels are clearly inverted....but only for the concreteness task
```{r}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0),
         Response.n = as.numeric(Response.n)) %>% 
  group_by(Switch,Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


What we can see from the following graph, is that the key labels are clearly inverted....
```{r}
agr <- d %>% 
  filter(Task == "Valence") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0),
         Response.n = as.numeric(Response.n)) %>% 
  group_by(Switch,Word) %>% 
  summarize(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow,
         YMax = PropPositive + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropPositive,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

